How to compute the fusion product of MV cycles in type A

### 2021-05-05 draft.tex
Edited Section 8
added some refs and added some stuff to 7.2

Let $ X_1, X_2 \subset \Gr$ be two subschemes, and consider the subscheme $ \tau^{-1}(X_1 \times X_2) \subset \Gr_{0, \CC^\times} $.
% 
% \jcom{I changed this a bit in order to match Mirkovi\'c--Vilonen better.}
% \acom{We say ``we define the subscheme..'' but what is there to define? Should it say ``we consider'' maybe?}
% Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
% 
We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  \tau^{-1}(X_1 \times X_2) $ inside of $ \Grbd $.  By construction, this is a flat family over $ \AA$.  We write $X_1 \ast_s X_2 $ for the scheme-theoretic fibre over a point $ s \in \AA$.

If $ s \ne 0$, then the map $ \tau_s$ identifies $ X_1 \ast_s X_2 \subset \Gr_{0,s}$ with $ X_1 \times X_2 \subset \Gr \times \Gr$.

On the other hand, the fibre $ X_1 \ast_0 X_2$ is a subscheme of $ \Gr_{0,0} $, but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.  We call this subscheme the \textbf{fusion} of $ X_1 $ and $ X_2$.

\jcom{I rewrote this to introduce the $ X_1 \ast_s X_2 $ notation that we need for later.  In doing so, $ X_1 \circ X_2 $ became obsolete, since we now have $ X_1 \ast_0 X_2$, but if you like we could just define $X_1 \circ X_2 = X_1 \ast_0 X_2 $.}

@@

\acom{Ah, sorry --- so do we introduce a even more general notion of $\ast_\AA$ for arbitrary flat families? Looking at Eisenbud's geoemtry of schemes (where flat iff tor-free actually shows up as Exercise II-33!) there does not seem to be anything quite like $\ast_\AA$ or $\circ$ defined.}

\jcom{I'm not sure how a general notion would be defined.  In our case, we are using the special fact that the general fibre is a product.}

\acom{I mean exactly in the case of this special fact, which is not special to the BD Gr.}

@@

Restricting to the zero fibre and applying $\tau_0$ we recover \cite[a main result]{dthesis}, itself a corollary of the ordinary affine Grassmannian version of \Cref{th:OGrl}, \cite[Theorem~4.4.1(c)]{mirkovic2019comparison}. 
% 
\begin{corollary}
    \label{cor:mvy}
    $\overline{\OO}^\lambda \cap \TT_\mu\cap\n \cong\overline\Gr^\lambda\cap S^\mu$. 
\end{corollary}
The irreducible components of the closure of the intersection on the righthand side are \textbf{MV cycles of type $\lambda$ and weight $\mu$}. By BKK the set of MV cycles of all possible types and weights can be glued together to form a \textbf{perfect basis} of $\CC[N]$.

@@

@@

In \cite{mvcycle}, the third author gave a combinatorial description of MV cycles for any reductive group, using Mirkovic-Vilonen polytopes, or equivalently Lusztig data.  For $ GL_m$, this description can be reworded in terms of Young tableaux. 
\jcom{Maybe add something here about Lusztig data and the standard reduced word.}

@@

Given $\tau\in YT(\lambda)_\mu$ and $ i \in \{1, \dots m\} $, denote by $\lambda(i)$ (resp.\ $\mu(i)$) the shape (resp.\ the weight) of $\tau(i)$, the tableau got from $\tau$ by discarding all boxes of weight exceeding $i$. (Note that $ \mu(i)$ only depends on $ \mu$, while $ \lambda(i)$ depends on the tableau $ \tau$.)  We will regard $ \lambda(i)$ (resp. $\mu(i)$) as an effective dominant coweight (resp. effective coweight) for $GL_i$. 
%

The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is a list of $ m(m-1)/2$ non-negative integers defined from its \textbf{Gelfand--Tsetlin pattern} $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ \acom{cite BZ} by the formula 
$$
n_\bullet(\tau)_{i,j} = \lambda(i+1)_j - \lambda(i)_j
$$
for $(i,j) = (1,1), (2,1), \dots, (m,1), (2,2),\dots,(m,2),\dots,(m,m)$. The pattern is recorded as a lower-triangular matrix (array of shapes of subtableaux) and the datum is recorded as a sequence.
\jcom{Something is wrong with the indexing of the Lusztig data, there should only be $ m(m-1)/2 $ entries.}

@@

The following result is closely related to Theorem 4 from \cite{dranowski2020generalized}.  It is also closely related to the description of MV cycles in terms of Kostant data obtained by Anderson-Kogan \cite{andersonkogan1} (see Section 9 in \cite{mvcycle}).  We also note that a different map from Young tableaux to MV cycles was obtained by Gaussent-Littelmann-Nguyen \cite[Theorem 2]{GLN}.
\begin{proposition}
    \label{pr:newmvdes}
    $Z(\tau)$ the MV cycle whose Lusztig datum with respect to $ \vi $ is $n_\bullet(\tau)$. 
\end{proposition}
\begin{proof}
    The proof of this theorem follows the same strategy as in \cite{dranowski2020generalized}.
\jcom{Maybe you would prefer to cite your thesis, Anne, but I think that it is better to cite the paper, since people can access it easier.}

@@

\jcom{Actually we will need this notation later when we talk about stable MV cycles.  Maybe we should change $ S^\mu $ to $S^\mu_-$.}

First, we consider
\begin{equation*}
Z(\tau)_1 := \{ L \in S^\mu : L \cap \cO^i \in S_+^{\lambda(i)} \text{ for } i = 1, \dots m\}  
%Z(\tau)_2 := \{ L \in S^\mu : L \cap \cO^i \in S^{\lambda(i)} \cap \Gr^{\lambda(i)} \text{ for } i = 1, \dots m\}
\end{equation*}
From Corollary 9.7 of \cite{mvcycle}, we see that $ Z(\tau)_1$ is equal to $ t^\mu A(n_\bullet(\tau))^T$, where $ A(n_\bullet)$ is defined in section 4.3 of \cite{mvcycle}.  Thus, $ \overline{Z(\tau_1)}$ is the MV cycle whose Lusztig datum is $ n_\bullet(\tau) $.  We also note that $Z(\tau_1) \subset \Gr^\lambda$ is dense in $ Z(\tau_1)$.  
\jcom{Need to justify this last sentence.}

@@

% 
% In this section we demonstrate how to put the main results of this paper into practice.
% 
% 
\subsection{Fusion of MVCs}
Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before, and take $\tau'\in YT(\lambda')_{\mu'}$ and $\tau''\in YT(\lambda'')_{\mu''}$. 
%

Given $A \in M_N(\CC)$ we denote by 
% $A\big|_{\CC^i}$ 
$A\big|_{\CC^p}$ 
the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors. If $A\big|_{\CC^p}$ preserves $\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$. 
% \acom{We may want to introduce $\ast_s$ in general. For now we make a definition.} 
Given $s\in\CC$, let 
\begin{equation*}
    X(\tau')\ast_s X(\tau'') = \left\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\right\}\,.
\end{equation*}
% 
% and let $Z'\ast_s Z'' = (Z'\ast_\AA Z'')_s$.
% If $s\ne 0$ identify $Z'\ast_s Z''= Z'\times Z''$ via $\Gr_{0,s}\cong \Gr\times\Gr$.
% \acom{or make the identification using the map the map $\tau$ of \Cref{eq:mvitau}. Can similarly identify $X'\ast_s X'' = X'\times X''$ by performing the obvious change of basis and block-diagonalizing. May make sense to introduce $\ast_s$ in greater generality, earlier; or at least on MV cycles earlier, since here I should actually make the definition for $Z(\tau)$'s.. which is ok, as in not a loss of generality. Still..}

@@

\begin{proof}
    % We wish to apply \Cref{prop:dth}. Nope
    % We will also need \Cref{le:Grl1l2}. Nope 
    % Consider the following diagram.
    % \[
    % \begin{tikzcd}
    %     X'\ast_s X'' \ar[r,dashed,"?"] \ar[d,"\bar g"] & X'\times X'' \ar[d," \phi\times \phi"] \\ 
    %     \Gr_{0,s}\ar[r,"\tau_s"] & \Gr\times\Gr
    % \end{tikzcd}
    % \]
    % \acom{Not sure what's a good notation for the vertical arrows. Don't want to introduce $\phi$. $\bar g(A) = g(A)\CC[t]^m$ temporarily.}
    % We show that the image of $\tau_s\circ \bar g$ coincides with the image of $\phi\times\phi$ which is dense in $Z'\times Z''$ by \Cref{prop:dth}.
    % % 
    Let $A\in X(\tau')\ast_s X(\tau'')$, let $i = 1,\dots, m$.  
    % Denote by 
    % $E_a$ the generalized $a$-eigenspace of $A$, and by 
    Clearly, the lattices $L=g(A)\CC[t]^m$ and $l=g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i$ are related by
    $$
    L\cap \CC[t]^i = l. 
    $$
    By definition of $X'\ast_s X''$,  $A\big|_{\CC^{|\mu(i)|}}$ has Jordan type $((\lambda'(i),0),(\lambda''(i),s))$ and lies in $\UU^{\mu'(i),\mu''(i)}_{0,s}$. So, by \Cref{th:OTGrW}, $l\in\Gr_{0,s}^{\lambda'(i),\lambda''(i)} \cong \Gr^{\lambda'(i)}\times \Gr^{\lambda''(i)}$ so $(l(0),l(s))\in Z(\tau')\times Z(\tau'')$.
\end{proof}
Let $X(\tau')\ast_0 X(\tau'')$ be the zero fibre of $\overline{\cup_{s\in\CC-0} X'\ast_s X''}$. 
\begin{itemize}
    \item $X'\ast_0 X'' \cong Z'\ast_0 Z''$ 
    \item $X'\ast_0 X''$ is a union of GOVs
    \item hence, $Z'\ast_0 Z''$ is a union of associated MVCs
\end{itemize}

What is a GOV? Let $X(\tau)$ be the top-dimensional \acom{speak to this?} irreducible component of
% from $\tau\in YT(\lambda)_\mu$ by 
\[
% X(\tau) = 
% \overline{
    \{
        A \in  \TT_\mu\cap\n : A\big|_{\CC^{|\mu(i)|}} \in \OO^{\lambda(i)} \text{ for each } i = 1,\dots,m
    \}\,. 
% }    
\]
$\overline{X(\tau)}$ is called a \textbf{generalized orbital variety}. 
% 
% By \cite[?]{dthesis}.
\begin{proposition}
    \label{pr:govsasirrecs}
    The irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ are $\{\overline{X(\tau)} : \tau\in YT(\lambda)_\mu\}$. 
\end{proposition}

\begin{proposition}(\cite{baumann2019mirkovic})
    % Given two MV cycles $Z_\tau$ and $Z_\sigma$ of type\dots 
    Let $Z',Z''$  be MV cycles of type $\lambda',\lambda''$ and weight $\mu',\mu''$ resp.\ and assume that $\lambda',\lambda'',\mu = \mu' + \mu''$ are dominant. 
    Then 
    \begin{equation}
        Z'\ast_0 Z'' = \cup Z(\tau)
        % \label{eq:tabmult}
        % % Z_\tau\ast Z_\sigma 
        % m_{\lambda'\lambda''} ([Z']\otimes[Z'']) 
        % = 
        % % \sum_{Z\in\cZ(\lambda)_\mu} 
        % \sum_{\tau\in S(\lambda)_\mu}
        % i\left(
        %     X(\tau), X(\tau')\circ X(\tau'')
        % \right) [Z(\tau)]\,. 
    \end{equation}
    with $i\left(X(\tau), X(\tau')\circ X(\tau'')\right)$ copies of $Z(\tau)$ showing up on the RHS. 
\end{proposition}
% 
\acom{Closures missing. Here and elsewhere}

>>>>

Let $ X_1, X_2 \subset \Gr$ be two subschemes, and consider the subscheme $ \tau^{-1}(X_1 \times X_2) \subset \Gr_{0, \CC^\times} $.
% 
% \jcom{I changed this a bit in order to match Mirkovi\'c--Vilonen better.}
% \acom{We say ``we define the subscheme..'' but what is there to define? Should it say ``we consider'' maybe?}
% Via the isomorphism $ \Gr_{0,s} \cong \Gr \times \Gr_s $,  for each $ s \ne 0$, we obtain a subscheme $ X_1 \times X_2 \times \AA^\times $  of $\Grbd$.  
% 
% We define $ X_1 \ast_{\AA} X_2 $ to be the scheme-theoretic closure of $  \tau^{-1}(X_1 \times X_2) $ inside of $ \Grbd $.  By construction, this is a flat family over $ \AA$.  We write $X_1 \ast_s X_2 $ for the scheme-theoretic fibre over a point $ s \in \AA$.

% If $ s \ne 0$, then the map $ \tau_s$ identifies $ X_1 \ast_s X_2 \subset \Gr_{0,s}$ with $ X_1 \times X_2 \subset \Gr \times \Gr$.

% On the other hand, the fibre $ X_1 \ast_0 X_2$ is a subscheme of $ \Gr_{0,0} $, but regarded as a subscheme of $ \Gr $ using {the isomorphism} $\Gr_{0,0} \cong \Gr $.  We call this subscheme the \textbf{fusion} of $ X_1 $ and $ X_2$.

% \jcom{I rewrote this to introduce the $ X_1 \ast_s X_2 $ notation that we need for later.  In doing so, $ X_1 \circ X_2 $ became obsolete, since we now have $ X_1 \ast_0 X_2$, but if you like we could just define $X_1 \circ X_2 = X_1 \ast_0 X_2 $.}

@@

% \acom{Ah, sorry --- so do we introduce a even more general notion of $\ast_\AA$ for arbitrary flat families? Looking at Eisenbud's geoemtry of schemes (where flat iff tor-free actually shows up as Exercise II-33!) there does not seem to be anything quite like $\ast_\AA$ or $\circ$ defined.}

% \jcom{I'm not sure how a general notion would be defined.  In our case, we are using the special fact that the general fibre is a product.}

% \acom{I mean exactly in the case of this special fact, which is not special to the BD Gr.}

@@

Restricting to the zero fibre and applying $\tau_0$ we recover \cite[a main result]{dthesis}, itself a corollary of the ordinary affine Grassmannian version of \Cref{th:OGrl}, \cite[Theorem~4.4.1(c)]{mirkovic2019comparison}. 
% 
\begin{corollary}
    \label{cor:mvy}
    $\overline{\OO}^\lambda \cap \TT_\mu\cap\n \cong\overline\Gr^\lambda\cap S^\mu$ where $\n\subset M_N(\CC)$ is the subalgebra of upper-triangular matrices. 
\end{corollary}
The closures of the irreducible components of the righthand side are \textbf{MV cycles of type $\lambda$ and weight $\mu$}. By \cite{baumann2019mirkovic} the set of MV cycles of all possible types and weights can be stitched together to form a \textbf{perfect basis} of $\CC[N]$.

@@

\acom{With this definition here what do we do about the sentence after \Cref{cor:mvy} above?}

@@

In \cite{kamnitzer2010mirkovic}, the third author gave a combinatorial description of MV cycles for any reductive group, using Mirkovic-Vilonen polytopes, or equivalently Lusztig data.  For $\GL_m$, this description can be reworded in terms of Young tableaux. 
\jcom{Maybe add something here about Lusztig data and the standard reduced word, $\vi = (1,2,\dots,m-1,\dots,1,2,1)$.}

@@

Given $\tau\in YT(\lambda)_\mu$ and $ i \in \{1, \dots m\} $, denote by $\lambda(i)$ (resp.\ $\mu(i)$) the shape (resp.\ the weight) of $\tau(i)$, the tableau got from $\tau$ by discarding all boxes of weight exceeding $i$. (Note that $ \mu(i)$ only depends on $ \mu$, while $ \lambda(i)$ depends on the tableau $ \tau$.)  We will regard $ \lambda(i)$ (resp. $\mu(i)$) as an effective dominant coweight (resp. effective coweight) for $\GL_i$. 
%

The Lusztig datum $n_\bullet(\tau)$ of the tableau $\tau$ is a list of $ m(m-1)/2$ non-negative integers defined from its \textbf{Gelfand--Tsetlin pattern} $\gt(\tau) = (\lambda(i)_j)_{1\le j\le i\le m}$ by the formula 
$$
n_\bullet(\tau)_{i,j} = \lambda(i+1)_j - \lambda(i)_j
$$
for $(i,j) = (1,1), (2,1), \dots, (m-1,1), (2,2),\dots,(m-1,2),\dots,(m-1,m-1)$. 
The pattern is recorded as a lower-triangular matrix (array of shapes of subtableaux) and the datum is recorded as a sequence. See \cite[\S 4]{berenstein1988tensor}.

\jcom{Something is wrong with the indexing of the Lusztig data, there should only be $ m(m-1)/2 $ entries.}

\acom{Yes $i = m$ doesn't make sense. Should be $i = 1,\dots,m-1$ and $j = 1\dots i$ or $(1,1),(2,1),..,(m-1,1),(2,2),..,(m-1,2),..,(m-1,m-1)$ which is $(m-1) + (m-1-1) + \cdots + 1$ things. Right?}

@@

The following result is closely related to Theorem 4 from \cite{dranowski2020generalized}.  It is also closely related to the description of MV cycles in terms of Kostant data obtained by Anderson--Kogan \cite{anderson2006algebra} \acom{is this the right AK?} (see Section 9 in \cite{kamnitzer2010mirkovic}).  We also note that a different map from Young tableaux to MV cycles was obtained by Gaussent--Littelmann--Nguyen \cite[Theorem 2]{gaussent2013knuth}.
\begin{proposition}
    \label{pr:newmvdes}
    $Z(\tau)$ is the MV cycle whose Lusztig datum with respect to $ \vi $ is $n_\bullet(\tau)$. 
\end{proposition}
\begin{proof}
    The proof of this theorem follows the same strategy as in \cite{dranowski2020generalized}.
\jcom{Maybe you would prefer to cite your thesis, Anne, but I think that it is better to cite the paper, since people can access it easier.}    
\acom{I've been meaning to update the paper. It's peppered with ``typos''.}

@@

\jcom{Actually we will need this notation later when we talk about stable MV cycles.  Maybe we should change $ S^\mu $ to $S^\mu_-$.}
\acom{For it.}

First, we consider
\begin{equation*}
Z(\tau)_1 := \{ L \in S^\mu : L \cap \cO^i \in S_+^{\lambda(i)} \text{ for } i = 1, \dots m\}  
%Z(\tau)_2 := \{ L \in S^\mu : L \cap \cO^i \in S^{\lambda(i)} \cap \Gr^{\lambda(i)} \text{ for } i = 1, \dots m\}
\end{equation*}
From \cite[Corollary 9.7]{kamnitzer2010mirkovic}, we see that $ Z(\tau)_1$ is equal to $ t^\mu A(n_\bullet(\tau))^T$, where $ A(n_\bullet)$ is defined in section 4.3 of \cite{kamnitzer2010mirkovic}.  Thus, $ \overline{Z(\tau_1)}$ is the MV cycle whose Lusztig datum is $ n_\bullet(\tau) $.  We also note that $Z(\tau_1) \subset \Gr^\lambda$ is dense in $ Z(\tau_1)$.  
\jcom{Need to justify this last sentence.} \acom{We mean $Z(\tau_1)\cap \Gr^\lambda$ is dense in $Z(\tau_1)$?}

@@

% 
% In this section we demonstrate how to put the main results of this paper into practice.
% 
% 
\subsection{Fusion of MVCs}
Let $m,\lambda',\lambda'',\lambda,\mu',\mu'',\mu,N$ be as before.
% 
Given $A \in M_N(\CC)$ we denote by 
% $A\big|_{\CC^i}$ 
$A\big|_{\CC^p}$ 
the restriction of $A$ to the subspace spanned by the first $p$ standard basis vectors. If $A\big|_{\CC^p}(\CC^p)\subset\CC^p$ then we identify it with the $p\times p$ upper-left submatrix of $A$. 
% \acom{We may want to introduce $\ast_s$ in general. For now we make a definition.}

Given $s\in\CC\setminus \{0\}$, and a pair of tableaux $\tau'\in YT(\lambda')_{\mu'}$ and $\tau''\in YT(\lambda'')_{\mu''}$ we define
\begin{equation*}
    X(\tau')\ast_s X(\tau'') = \left\{A\in\UU_{0,s}^{\mu',\mu''} : A \big|_{\CC^{|\mu(i)|}} \in \OO_{0,s}^{\lambda'(i),\lambda''(i)} \text{ all } i=1,\dots,N\right\}\,.
\end{equation*}
% 
% and let $Z'\ast_s Z'' = (Z'\ast_\AA Z'')_s$.
% If $s\ne 0$ identify $Z'\ast_s Z''= Z'\times Z''$ via $\Gr_{0,s}\cong \Gr\times\Gr$.
% \acom{or make the identification using the map the map $\tau$ of \Cref{eq:mvitau}. Can similarly identify $X'\ast_s X'' = X'\times X''$ by performing the obvious change of basis and block-diagonalizing. May make sense to introduce $\ast_s$ in greater generality, earlier; or at least on MV cycles earlier, since here I should actually make the definition for $Z(\tau)$'s.. which is ok, as in not a loss of generality. Still..}

@@

\begin{proof}
    % We wish to apply \Cref{prop:dth}. Nope
    % We will also need \Cref{le:Grl1l2}. Nope 
    % Consider the following diagram.
    % \[
    % \begin{tikzcd}
    %     X'\ast_s X'' \ar[r,dashed,"?"] \ar[d,"\bar g"] & X'\times X'' \ar[d," \phi\times \phi"] \\ 
    %     \Gr_{0,s}\ar[r,"\tau_s"] & \Gr\times\Gr
    % \end{tikzcd}
    % \]
    % \acom{Not sure what's a good notation for the vertical arrows. Don't want to introduce $\phi$. $\bar g(A) = g(A)\CC[t]^m$ temporarily.}
    % We show that the image of $\tau_s\circ \bar g$ coincides with the image of $\phi\times\phi$ which is dense in $Z'\times Z''$ by \Cref{prop:dth}.
    % % 
    Let $A\in X(\tau')\ast_s X(\tau'')$ and $i = 1,\dots, m$.  
    % Denote by 
    % $E_a$ the generalized $a$-eigenspace of $A$, and by 
    The lattices $L=g(A)\CC[t]^m$ and $l=g(A\big|_{\CC^{|\mu(i)|}})\CC[t]^i$ are related by
    $$
    L\cap \CC[t]^i = l
    $$
    where $\CC[t]^i\subset\CC[t]^m = \CC^m\otimes_\CC\CC[t]$ denotes the $\CC[t]$-submodule generated by the first $i$ standard basis vectors.
    %

By definition of $\UU^{\mu',\mu''}$ we have $A\big|_{\CC^{|\mu(i)|}}\in\UU^{\mu'(i),\mu''(i)}_{0,s}$ and by definition of $X(\tau')\ast_s X(\tau'')$, $A\big|_{\CC^{|\mu(i)|}}$ has Jordan type $((\lambda'(i),0),(\lambda''(i),s))$. So, by \Cref{th:OTGrW}, $l\in\Gr_{0,s}^{\lambda'(i),\lambda''(i)}$ and
% \Gr^{\lambda'(i)}\times \Gr^{\lambda''(i)}$ so 
$(l(0),l(s))\in Z(\tau')\times Z(\tau'')$.
\end{proof}
% 
% 
In analogy with the BD construction \acom{add loc cit} we define $X(\tau')\ast_0 X(\tau'')$ to be the zero fibre of the family $\overline{\bigcup_{s\in\CC\setminus\{0\}} X(\tau')\ast_s X(\tau'')}$ in $M_N(\CC)$. 
% 
\begin{corollary}
    $X'\ast_0 X'' \cong Z'\ast_0 Z''$ 
\end{corollary}
% 
Let $X(\tau)$ be the top-dimensional \acom{speak to this?} irreducible component of
% from $\tau\in YT(\lambda)_\mu$ by 
\[
% X(\tau) = 
% \overline{
    \{
        A \in  \TT_\mu\cap\n : A\big|_{\CC^{|\mu(i)|}} \in \OO^{\lambda(i)} \text{ for each } i = 1,\dots,m
    \}\,. 
% }    
\]
Then $\overline{X(\tau)}$ is called a \textbf{generalized orbital variety}. 
%

\begin{theorem}
    \label{pr:govsasirrecs}
    The irreducible components of $\overline{\OO}^\lambda\cap\TT_\mu\cap\n$ are $\{\overline{X(\tau)} : \tau\in YT(\lambda)_\mu\}$. 
\end{theorem}
\acom{$\overline{X(\tau)}$ vs $Z(\tau) = \overline{al;sdj}$}
\begin{corollary}
    $X'\ast_0 X''$ is a union of GOVs.
\end{corollary}
\begin{proof}
    Since $X'\ast_0 X''\subset \overline{\OO}^\lambda\cap\TT_\mu\cap\n$\dots 
\end{proof}

\begin{proposition}(\cite{baumann2019mirkovic})
    % Given two MV cycles $Z_\tau$ and $Z_\sigma$ of type\dots 
    Let $Z',Z''$  be MV cycles of type $\lambda',\lambda''$ and weight $\mu',\mu''$ resp.\ and assume that $\lambda',\lambda'',\mu = \mu' + \mu''$ are dominant. 
    Then $Z'\ast_0 Z''$ is a union of MVCs
    % \begin{equation}
        % Z'\ast_0 Z'' = \bigcup Z(\tau)
        % \label{eq:tabmult}
        % % Z_\tau\ast Z_\sigma 
        % m_{\lambda'\lambda''} ([Z']\otimes[Z'']) 
        % = 
        % % \sum_{Z\in\cZ(\lambda)_\mu} 
        % \sum_{\tau\in S(\lambda)_\mu}
        % i\left(
        %     X(\tau), X(\tau')\circ X(\tau'')
        % \right) [Z(\tau)]\,. 
    % \end{equation}
    with $i\left(X(\tau), X(\tau')\circ X(\tau'')\right)$ copies of $Z(\tau)$ showing up. 
\end{proposition}
% 
\acom{Closures missing? Here and elsewhere?}
% 
\begin{proof}
    Since $X'\ast_0 X'' \cong Z'\ast_0 Z''$ and GOVs go to MVCs 
\end{proof}
